Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-11 paper.qmd
Updated Figure 15 a)

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(data = tsne_minst_scaled,
             aes(
               x = tSNE1,
               y = tSNE2
             ),
             alpha=0.5, 
             size = 0.1) +
  coord_fixed() +
  interior_annotation("a", sc_ltr_pos_mnist)

>>>>

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c",
               linewidth = 1) +
  geom_point(data = tsne_minst_scaled,
             aes(
               x = tSNE1,
               y = tSNE2
             ),
             alpha=0.1) +
  interior_annotation("a", sc_ltr_pos_mnist) +
  theme(aspect.ratio = 1)
